---
title: "Setup"
author: "Jenny Sjaarda"
date: "2019-12-20"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

This directory was setup by following the steps below

```{r eval=FALSE}

setwd("Dropbox/gitrepos")
library("workflowr")
project_name <- "future_reference"
wflow_start(project_name) # creates directory called project_name

wflow_build() # create directories

wflow_publish(c("analysis/index.Rmd", "analysis/about.Rmd", "analysis/license.Rmd"),
              "Publish the initial files for myproject")

wflow_use_github("jennysjaarda") # select option 2: manually create new repository on github 

wflow_git_push()

```

To maintain the website the general workflow outlined by [workflowr](https://jdblischak.GitHub.io/workflowr/articles/wflow-01-getting-started.html#the-workflow) were followed: 

  1. Open a new or existing R Markdown file in `analysis/` (optionally using `wflow_open()`). If creating manually, add the following to the top of the R Markdown file with an appropriate name for `Title`:
  
```{r eval=FALSE}
---
title: "Title"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
---
```

  2. Write documentation in the R Markdown file.

  3. Run `wflow_build()` to view the results as they will appear on teh website (alternatively press the Knit button in RStudio).

  4. Go back to step 2 until satisfied. 
  
  5. Run `wflow_publish()` to commit the sourcefile.
  
  6. Push the changes to GitHub with `wflow_git_push()` (or `git push` in Terminal).

  7. Use `wflow_status()` to track repository.
